A pipeline to analyse time-course gene expression data

### 2019-08-12 scripts/manuscript.Rmd
FIX names.arg doesn't work on my computer

    barplot(number_de_genes_per_time, col="black", 
            # names.arg=labels,
	    ylim=c(0, 20000),
	    xlab="Timepoint", ylab="Number of DE genes", main=title, ...)  
}

par(mfrow=c(2, 2))
timely_barplot(K_weekly_de_analysis, time, title="Kawasaki", las=3)
timely_barplot(C_weekly_de_analysis, time, title="California", las=3)
timely_barplot(VL_weekly_de_analysis, time, title="Vietnam low-dose", las=3)
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high-dose", las=3)
```

>>>>

    barplot(number_de_genes_per_time, col="black", 
            names.arg=labels,
	    ylim=c(0, 20000),
	    xlab="Timepoint", ylab="Number of DE genes", main=title, ...)  
}

par(mfrow=c(2, 2))
timely_barplot(K_weekly_de_analysis, time, title="Kawasaki", las=3)
timely_barplot(C_weekly_de_analysis, time, title="California", las=3)
timely_barplot(weekly_de_analysis, time, title="Vietnam low-dose", las=3)
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high-dose", las=3)
```
